Proportional multi-state multiple-cohort life table model

### 2018-04-17 MSLT/MSLTdoc.Rmd
Loop graphs  names
Plots
Sort data

4) Read GBD data
```{r, echo=TRUE}
GBDdata <- read.csv("data/IHME-GBD_2016_DATA-8fca12f6-1.csv", stringsAsFactors = F)
```

@@

14) Generate graphs are to compare GBD data for England and Greater London.

@@

```{r, echo=FALSE}
#Call plots here, add titles to figures

>>>>

4) Read GBD data
```{r, echo=TRUE}
GBDdata <- read.csv("MSLT/data/UK/englandandgreaterlondon.csv", stringsAsFactors = F)
```

@@

14) Generate graphs to compare GBD data for England and Greater London.

@@

FIX GRAPHS TITLES.
